---
title: "respirometry_hinal"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

# Load libraries

```{r,message=FALSE}
library(ggplot2)
library(dplyr)
library(data.table)
library(lubridate)
library(MASS)
```





# Load data

WE want to load the data and calculate quick and dirty mass specific metabolism (with not accounting for hours just yet; so no rate)

```{r hinal}

resp<-fread("../Data/2018-09-07_Hinal_diapause_determination.csv")
dim(resp)
head(resp)

#convert purge times to units in hours
resp$purge_time<-hour(hm(resp$Purge_time))+minute(hm(resp$Purge_time))/60
```


# calculating purge time

we need to create a sequence of purge times that are the length of the cohorts

```{r, echo=FALSE,include=FALSE}
resp$cohort_date<-as.factor(resp$cohort_date)
test<-filter(resp,cohort_date=="9/29/18" & tape=="red")
#filter(resp,cohort_date=="9/29/18")

start<-min(test$purge_time,na.rm=TRUE)
finish<-max(test$purge_time,na.rm=TRUE)
n<-length(test$purge_time)

seq(from=start,to=finish,length.out=n)
```

# Data manipulation and calculating resp rate

```{r}
#figuring out sample sizes per host, tape, cohort,and resp day
#resp%>%
 # dplyr::group_by(Host,tape,cohort_date,day_resp)%>%
  #summarise(n=length(tape))

#w e figured out purge time 
resp.1<-resp%>%
  dplyr::group_by(Host,tape,cohort_date,day_resp)%>%
  mutate(full_purge_time=seq(from=min(purge_time,na.rm=TRUE),to=max(purge_time,na.rm=TRUE),length.out=length(purge_time)))

#names(resp.1)
#resp.1$full_purge_time

### now we need total time 

#resp.1$Respiration_time

resp.1$resp_time1<-hour(hms(resp.1$Respiration_time)) + minute(hms(resp.1$Respiration_time))/60+second(hms(resp.1$Respiration_time))/360

resp.1$total_time<- (24-resp.1$full_purge_time) +resp.1$resp_time1


### now that we have total time in syringe, we can measure metablic rate (CO2/time)

## we first need to subtract every value by blank 

blank<-resp.1%>%
  dplyr::group_by(Host,tape,cohort_date,day_resp)%>%
  filter(Sample=="b")%>%
  summarize(blank=mean(Respiration))

# To look at the negative resp values 
#filter(resp.1,Respiration<0)
#join smaller blank dataset with larger dataset  
resp.2<-inner_join(resp.1,blank,by=c("Host","tape","cohort_date","day_resp"))
#cbind(resp.2$Respiration,resp.2$blank)
#subtract rows!
resp.2$norm_resp<-resp.2$Respiration-resp.2$blank


####Calculating metabolic rate and mass specific metabolic rate

resp.2$MR<- resp.2$norm_resp/resp.2$total_time # metabolic rate
resp.2$MSMR<- resp.2$norm_resp/(resp.2$total_time*resp.2$weight)# mass specific metabolic rate
resp.2<-filter(resp.2,Sample=="e")

```




## Make plots of the data

```{r}
#mass specific metabolic rate
ggplot(resp.2,aes(x=MSMR,fill=Host))+geom_histogram(position="identity")+facet_wrap(day_resp~cohort_date,scale="free")+geom_vline(xintercept=0.0025)

#metabolic rate
ggplot(resp.2,aes(x=MR,fill=Host))+geom_histogram(position="identity")+facet_wrap(day_resp~cohort_date,scale="free")+geom_vline(xintercept=0.02)

```

### Assigning cutoffs for diapause and non-diapause 

```{r}
# 2 cutoffs and let's see how they match 
resp.2$cutoffMSMR<-ifelse(resp.2$MSMR<0.0025,"Diapause","Non-Diapause")

resp.2$cutoffMR<-ifelse(resp.2$MR<0.02,"Diapause","Non-Diapause")

table(resp.2$cutoffMR,resp.2$cutoffMSMR)

#how many non-diapausers across days and host? 
resp.2%>%
  group_by(Host,day_resp,cutoffMSMR)%>%
  summarise(sample.size=length(Host))%>%
  knitr::kable()

resp.sum<-resp.2%>%
  group_by(Host,day_resp,cohort_date,cutoffMR)%>%
  summarise(sample.size=length(Host))%>%
  data.frame()
  #knitr::kable()

#resp.sum

#ggplot(resp.sum,aes(x=day_resp,y=sample.size,colour=factor(cutoffMR)))+geom_point(size=5)+geom_line(size=2)+facet_grid(.~Host)
ggplot(resp.sum,aes(x=factor(day_resp),y=sample.size,colour=paste(cutoffMR,Host)))+geom_boxplot()

#mod1<-glm(sample.size~day_resp*cutoffMR*Host,family=poisson(link="log"),data=resp.sum)
mod1<-glm.nb(sample.size~day_resp*cutoffMR*Host,data=resp.sum)

summary(mod1)

```


# Session info

```{r}
sessionInfo()
```