---
title: "Workflow_viability_selection"
output:
  html_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

# Library

```{r}
library(DiagrammeR)
```

# Overall Workflow

```{r}
mermaid("
  graph TD
  A[Master Data Sheet]--Calculate-->B[Metablic Rates CO2 production per hr per mass]
  B --> T[Day 11]
  B --> R[Day 15]
  A --Calculate--> C[Lifespan]
  T --> E[Scatter plot showing relationship between lifespan and mr]
  R --> E
  C --> E
          ")
```

## Detailed workflow for calculating metabolic rate  

How do we calculate metabolic rate? 

Metabolic rate = Co2 production / hours

Mass specific metabolic rate = Co2 production/hour/mass or Co2 production/(hour * mass)

What are cohorts? 

These are essentially handling replicates because we cannot sample all of the flies at once. For each cohort, there are two batches: 1 for licor 7000, and 1 for licor 6262. To process more samples, we spread out our measurements across 2 respirometers(licors). Each licor, has an associated tape color in the tape column. When we purged (purging = letting pupae breath in a syringe under standardized air without CO2), there was a start time and end time for the beginning and end of the purge for each tape samples(aka licor batch). 

What columns do we need from the master data sheet? 

* mass_day10 : mass at day 10 in mgs
* purge_time_1  : initial time for pupae in tube to breath 
* resp_time_1 : time of sampling for respirometry
* resp_day11 : respirometry at day 11

**The problem** with purge_time_1 is that besides cohort 1 for apple, there is only start and stop times for each cohort and color.
**The solution** is to create a time sequence for each cohort from start to end. 


```{r}
mermaid("
  graph TD
  A[Master data Sheet] --> B[Create time sequence for purge_time_1 in hours minutes]
  B --Subtract from 24 and add to resp_time_1--> C[Total hours]
  C --multiply by mass and divide over resp_day11--> D[Mass specific metabolic rate]      
  C --divide over resp_day11-->  V{Metabolic rate}
        ")

```


# Session Info

```{r}
sessionInfo()
```