---
title: "calculating mass specific metabolic rate"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

# Goal: calculate and visualize mass specific metabolic rate  

resp(mL)/time(hr)/mass(mg) =mass specific metabolic rate 


Then we want to compare it between apples and hawthornes   

reading in the data   

```{r}
library(lubridate)
library(dplyr)
library(ggplot2)


#dat<-read.csv("../Data/2018-08-07_master_data_slice.csv")
dat<-read.csv("2018-09-20_test_flies_only_eclosions.csv")
str(dat)
```


## Calculate total time 

### convert time (house:minutes:seconds) to units of hours 

### total time = (24-initial)+ respiormetry_time 
### day 11
```{r}
####creating a sequence for the purge times
dat$purge1_conv<-hour(hm(dat$purge_time_1))+minute(hm(dat$purge_time_1))/60
library(plyr)
ddply(dat,.(collection_date,cohort_day,tape),summarize,sample_sample=length(tape))
dat$purge2_conv<-hour(hm(dat$purge_time_2))+minute(hm(dat$purge_time_2))/60
#seq(from=min(dat$purge1_conv,na.rm=TRUE),to=max(dat$purge1_conv,na.rm=TRUE),length.out=length(dat$tape))
#dat2<-ddply(dat,.(collection_date,cohort_day,tape),transform,purge1_seq=seq(from=min(purge1_conv,na.rm=TRUE),to=max(purge1_conv,na.rm=TRUE),length.out=length(tape)))
dat2<-ddply(dat,.(collection_date,cohort_day,tape),transform,purge1_seq=seq(from=min(purge1_conv,na.rm=TRUE),to=max(purge1_conv,na.rm=TRUE),length.out=length(tape)),purge2_seq=seq(from=min(purge2_conv,na.rm=TRUE),to=max(purge2_conv,na.rm=TRUE),length.out=length(tape)))

###for the resp times, we just need to convert to hours 
dat2$resp1_seq<-hour(hms(dat$resp_time_1))+minute(hms(dat$resp_time_1))/60

dat2$total_time<-(24-dat2$purge1_seq)+dat2$resp1_seq


dat2$resp2_seq<-hour(hms(dat$resp_time_2))+minute(hms(dat$resp_time_2))/60

dat2$total_time2<-(24-dat2$purge2_seq)+dat2$resp2_seq
```


## Subtract out blanks from each sample for every collection date, cohort day, and tape color  

```{r}
blank.dat<-subset(dat2,Site_name=="Blank")

blank<-ddply(blank.dat,.(collection_date,cohort_day,tape),summarize,blank11=mean(resp_day11,na.rm=TRUE),blank15=mean(resp_day15,na.rm=TRUE))
#temporarily adding values for blank cohort 12 haws; day 15 resp
blank[44,5]<-blank[44,4]
blank

dat3<-left_join(dat2,blank,by=c("collection_date","cohort_day","tape"))
dim(dat3)

dat3$resp1_sub<-dat3$resp_day11-dat3$blank11
dat3$resp2_sub<-dat3$resp_day15-dat3$blank15
#head(cbind(dat3$resp_day11,dat3$resp1_sub,dat3$blank11))


```


## Actually doing the caluclation : 

```{r}
###metabolic rate
dat3$MR11<-dat3$resp1_sub/dat3$total_time
dat3$MR15<-dat3$resp2_sub/dat3$total_time

### mass specific metabolic rate
dat3$MSMR11<-dat3$resp1_sub/dat3$total_time/dat3$mass_day10
dat3$MSMR15<-dat3$resp2_sub/dat3$total_time/dat3$mass_day14

dat4<-subset(dat3,Site_name!="Blank" &  Resp_code == 1 & MSMR11 > 0 & organism!="wasp") # excluding blanks, wasps, msmr below 0, and experimental ones that don't have both day 11 and day 15

dim(dat4)
```

# Visualize MSMR    

```{r}
ggplot(dat4,aes(x=Host,y=MSMR11))+geom_boxplot()

#ggplot(dat4,aes(x=MSMR11,y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+xlim(0,.01)+facet_grid(.~factor(Li.cor_1))+ylim(0,90)


#day 11
ggplot(dat4,aes(x=MSMR11,y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+xlim(0,.015)+ylim(0,90)+xlab("Mass specific metabolic rate (mL/hr/mg)")

ggplot(dat4,aes(x=log10(MSMR11),y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+ylim(0,90)+xlab("Mass specific metabolic rate (mL/hr/mg)")+xlim(-3.5,-1.99)

summary(lm(eclosion_days~log10(MSMR11),data=dat4))

hist(resid(lm(eclosion_days~log10(MSMR11),data=dat4)))


summary(lm(eclosion_days~log10(MSMR15),data=dat4))

#day 15
ggplot(dat4,aes(x=MSMR15,y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+ylim(0,90)+xlab("Mass specific metabolic rate (mL/hr/mg)")+xlim(0,.01)

##day 11 vs day 15

ggplot(dat4,aes(x=MSMR11,y=MSMR15,colour=factor(cohort_day)))+geom_point(size=5)


###subtracting day11-day15
dat4$MSMR_diff<-dat4$MSMR11-dat4$MSMR15
#ggplot(dat4,aes(x=MSMR_diff,y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+ylim(0,90)+xlab("Mass specific metabolic rate (mL/hr/mg)")+xlim(-.015,.01)


###eclosion days
ggplot(dat4,aes(x=eclosion_days,fill=Host))+geom_histogram(alpha=.5,position="identity")

ggplot(dat4,aes(x=eclosion_days,fill=Host))+geom_density(alpha=.5,position="identity")

#ggplot(dat4,aes(x=factor(Li.cor_1),y=MSMR11))+geom_boxplot()
```

# Visualize metabolic rate   

```{r}

#day 11
ggplot(dat4,aes(x=MR11,y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+ylim(0,90)+xlab("metabolic rate (hr/mg)")+xlim(0,.1)

#day 15
ggplot(dat4,aes(x=MR15,y=eclosion_days,colour=Host))+geom_point(,size=5)+stat_smooth()+ylim(0,90)+xlab("metabolic rate (hr/mg)")+xlim(0,.1)



```


# Statistical analyses   
### discriminant analysis using weights, eclosion days, MR to class individuals into diapause or non-diapause   

```{r lda analysis }
names(dat4)

trait1<-dat4[,c("MSMR11","MSMR15","mass_day10","mass_day14","MR11","MR15","eclosion_days")]
head(trait1)
dim(trait1)
dim(na.omit(trait1))
trait2<-na.omit(trait1)

library(MASS)
#specifying groups    
trait2$groups<-ifelse(trait2$MR15< 0.00375,ifelse(trait2$eclosion_days<35,"non-diapause_lowMR","diapause"),"non-diapause_highMR")

fit1<-lda(groups~mass_day10+mass_day14+MR11+MR15+eclosion_days,data=trait2,CV=TRUE)
fit1
fit2<-qda(groups~mass_day10+mass_day14+MR11+MR15+eclosion_days,data=trait2,CV=FALSE)
#cbind(as.character(fit1$class),trait2$groups)

#predict.lda(oject=fit1,newdata=trait2[,3:7])
trait3<-data.frame(trait2,predict=as.character(predict(fit1)$class),ld1=predict(fit1)$x[,1],ld2=predict(fit1)$x[,2])
#trait4<-data.frame(trait2,predict=as.character(predict(fit2)$class),ld1=predict(fit2,b)$x[,1],ld2=predict(fit2)$x[,2])


# based on predictions 
ggplot(trait3,aes(x=ld1,y=ld2,colour=predict))+geom_point(size=5)
ggplot(trait3,aes(x=ld1,fill=predict))+geom_histogram(alpha=.25,position="identity") 

#comparing to pre-set designations   
ggplot(trait3,aes(x=ld1,y=ld2,colour=groups))+geom_point(size=5)

table(trait3$predict,trait3$groups)
nrow(trait3)
(21+120+4)/(145+17+2+26+3)

```


#### messing with time intervals   

```{r}

t<-interval("2017-11-01 00:01:00","2017-11-13 23:00:00", tzone = tz(start))
t

s<-seq(as.Date("2017-09-01"),by="days",length.out=100)
s

x<-read.table("../Data/raw/Trikinetics/Monitor6.txt")
x$V3<-match(x$V3,month.abb)


head(x)
time<-paste(paste("20",x$V4,"-",x$V3,"-",x$V2,sep=""),x$V5)

test<-data.frame(time=strptime(time,"%Y-%m-%d %H:%M:%S",tz=tz(start)))
head(test)


head(subset(test,time %within% t))

test[test$time %within% t,]
```



### Session Info

```{r}
sessionInfo()
```

